Target Markdown

### 2023-10-13 _targets.Rmd
Compute slope richness for async and pop_stab

@@

@@

```{r}
tar_load(model_fw_stab_scaled_coeff)

@@

```{r}
model_fw_stab_scaled_coeff %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(x = estimate, y = term, xmin = lower_ci, xmax = upper_ci)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
```

>>>>

  tar_target(pred_stab_comp_rho,
    fix_fw_stab_comp %>%
      left_join(
          response = fix_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
        left_join(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(0.01, 0.2, length.out = 50),
              seq(1.5, 3.5, length.out = 50),
              seq(.02, .3, length.out = 50)

@@

    mutate(slope = pmap(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          names(param) <- c("rho", param_name)

          encaps_get_slope_change(
            param_list = param,
            coeff_data = coeff,
            slope_term = "richness",
            default_variable_values = c(
              "rho" = 0,
              "env_stoch" = .1,
              "ct_alive" = .2,
              "avg_int_strength" = .01,
              "h" = 2,
              "w_avg_tlvl" = 1.5,
              "Z" = 100
            )
          )
        }
        )
    ) %>%
    select(-fix_effect, -values)
  )
)
```

@@

```{r}
tar_load(fix_fw_stab)
tar_load(fix_fw_stab_comp)

```{r}
tar_load(model_fw_stab_comp_scaled_coeff)

@@

```{r}
model_fw_stab_comp_scaled_coeff %>%
  unnest(cols = c(coeff)) %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(
      y = term, x = estimate,
      xmin = lower_ci, xmax = upper_ci,
      color = response)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
```

```{r}
p_model_fw_stab_com <- model_fw_stab_comp_scaled_coeff %>%
  filter(response == "stab_com") %>%
  unnest(cols = c(coeff)) %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(
      y = term, x = estimate,
      xmin = lower_ci, xmax = upper_ci
      )) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
ggsave_multiple(
  paste0("p_model_fw_stab_com", c(".png", ".pdf")),
  plot = p_model_fw_stab_com,
  path = here::here("report", "figures"),
  scale = 1.8,
  dpi = 400,
  width = 80,
  height = 80 * 1.3,
  units = "mm")
```
